\title{Incremental Value of Daily Workload and Wellness Monitoring Beyond a Personalised Readiness-History Baseline for Next-Calendar-Day Readiness in Elite Women's Football}

\author{Haoyang Cheng\\[0.25em]
\small Wuhan Sport University, Wuhan, China\\
\small ORCID: \href{https://orcid.org/0009-0009-4123-2610}{0009-0009-4123-2610}\\
\small Correspondence: Haoyang Cheng, \href{mailto:1303615018@qq.com}{\texttt{1303615018@qq.com}}}
\date{}

\maketitle

\begin{abstract}
\textbf{Purpose:} Daily workload and wellness monitoring are widely used in elite football, yet it remains uncertain whether a larger monitoring panel improves short-horizon readiness forecasts beyond current readiness and a player's own earlier forecast errors. We assessed the incremental forecasting value of a daily workload--wellness panel for next-calendar-day self-reported readiness in elite women's football, including a two-team transportability assessment under sequential personalisation.

\textbf{Methods:} This secondary analysis used publicly available SoccerMon subjective-monitoring data from 50 players in two elite women's football teams. The primary paired-comparison cohort comprised 14,582 player-day pairs with a complete current-day readiness and wellness profile, observed next-day readiness, and the 7-day load history used by the full model. Predictors available by the end of calendar day $t$ forecast readiness at $t+1$. A current-readiness population model (\Pzero) and a full-monitoring population model (\Pone) were each tuned in three expanding chronological source-team 2020 folds. Both models then received the same reset, past-only, player-specific residual adjustment during 2021 testing. Models were evaluated within teams and bidirectionally across teams. The primary estimand was \DeltaMAE{} = MAE(\Pone) $-$ MAE(\Pzero), with percentile 95\% player-cluster bootstrap confidence intervals.

\textbf{Results:} The full monitoring model did not reduce mean absolute error in any evaluation setting. \DeltaMAE{} was +0.007 (95\% CI $-$0.005 to +0.023) within Team A, +0.018 ($-$0.005 to +0.047) within Team B, +0.022 ($-$0.005 to +0.053) from Team A to Team B, and +0.004 ($-$0.007 to +0.016) from Team B to Team A. Positive values indicate higher error for \Pone. Results were directionally consistent across residual-history windows, a reduced-panel comparison, and an wellness-item-missingness sensitivity analysis conditional on observed current- and next-day readiness.

\textbf{Conclusions:} For report-complete player-days in these two elite women's football teams, the evaluated daily workload--wellness panel did not demonstrate stable incremental MAE improvement beyond a personalised readiness-history baseline with identical sequential residual updating. This finding does not imply that workload or wellness are causally irrelevant; rather, it challenges the assumption that adding routine daily variables necessarily improves next-calendar-day self-reported readiness forecasts in this deployment setting.
\end{abstract}

\textbf{Keywords:} athlete monitoring; women's football; readiness to train; training load; wellness; personalised forecasting; transportability
