\section*{Data availability}
The SoccerMon data used in this study are publicly available from Zenodo under a CC BY 4.0 licence: \url{https://doi.org/10.5281/zenodo.10033832}. The original SoccerMon data are not redistributed in this manuscript archive. The analysis code reconstructs the analytic player-day dataset from the official source archive. To avoid duplicate redistribution of player-level data, derived player-day data and individual prediction files are not included; non-identifying aggregate expected outputs are included for verification.

\section*{Code availability}
The analysis code, manuscript source, figures, tables, and non-identifying reproducibility materials are prepared as the immutable v1.1.2 release. Insert the version-specific Zenodo DOI here after the GitHub v1.1.2 release has been archived: \texttt{[Zenodo version DOI for v1.1.2 to be inserted]}. The public project repository is available at \href{https://github.com/chy010321/next-day-readiness-womens-football}{GitHub}. The v1.1.2 release replaces the manuscript Figure~1 artwork with a content-rich methodological pipeline and updates release documentation; it introduces no new numerical analysis and does not change audited primary or wellness-item-missingness estimates. The original SoccerMon data must be downloaded separately from Zenodo and are not redistributed in the code archive.

\section*{Ethics statement}
This study was a secondary analysis of publicly available, de-identified data and did not involve direct recruitment, interaction, intervention, or access to identifiable information. No additional ethics approval was obtained for this secondary analysis. The original SoccerMon data collection, including participant consent and applicable ethics and data-protection procedures, is described by Midoglu et al. \citep{Midoglu2024}.

\section*{Use of artificial intelligence}
Generative artificial intelligence tools, including ChatGPT, were used for language refinement, manuscript organisation, and draft code assistance. They were not authors and did not make analytical decisions. The author reviewed and verified the analytical decisions, statistical outputs, references, interpretation, and final manuscript content and takes full responsibility for the work. This disclosure should be adapted to the policy of the target journal.

\section*{Author contributions}
Haoyang Cheng: Conceptualization; Methodology; Software; Data curation; Formal analysis; Validation; Visualization; Writing---original draft; Writing---review \& editing.

\section*{Funding}
This research received no specific grant from any funding agency in the public, commercial, or not-for-profit sectors.

\section*{Competing interests}
The author declares no competing interests.

\section*{Acknowledgements}
The author acknowledges the SoccerMon authors and participating clubs for making the de-identified dataset publicly available.
